\documentclass{beamer}
\usepackage{graphicx}
\usepackage{fontawesome}
\usepackage{colortbl}
\usepackage{xcolor}

% Define colors for better styling
\definecolor{myblue}{RGB}{39, 56, 89}
\definecolor{mygreen}{RGB}{60, 179, 113}
\definecolor{mygray}{RGB}{169, 169, 169}

\title{Understanding Web Development}
\author{Idriss Bado}
\date{\today}

\begin{document}

% Title slide
\begin{frame}
  \titlepage
  \vspace{0.5cm}
  \centering
  
\end{frame}

% Slide 1: How Does the Web Work?
\begin{frame}
  \frametitle{How Does the Web Work?}
  \begin{itemize}
    \item \textbf{Client-Server Model:} The web operates on this model where the client (browser) sends requests to the server (web host).
    \item \textbf{Communication via HTTP:} The client communicates with the server using the HTTP protocol.
    \item \textbf{Content Delivery:} The server processes the request and returns data (HTML, CSS, JavaScript) to the client.
    \item \textbf{Example:} When you type a URL, the browser sends a request to the server, which responds with a webpage.
  \end{itemize}
  \vspace{0.5cm}

\end{frame}

% Slide 2: What Do You Need to Be a Web Developer?
\begin{frame}
  \frametitle{What Do You Need to Be a Web Developer?}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \textbf{Technical Skills:}
      \begin{itemize}
        \item HTML, CSS, JavaScript
        \item Frameworks (React, Angular, Vue.js)
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \textbf{Tools:}
      \begin{itemize}
        \item \faIcon{code} \textbf{Code Editors:} VSCode, Sublime Text
        \item \faIcon{git} \textbf{Version Control:} Git
      \end{itemize}
    \end{column}
  \end{columns}
  \vspace{0.5cm}
  
\end{frame}

% Slide 3: Why Did You Choose to Learn Web Development?
\begin{frame}
  \frametitle{Why Did You Choose to Learn Web Development?}
  \begin{itemize}
    \item \textbf{Creativity:} Fascination with creating interactive, user-friendly websites.
    \item \textbf{Career Growth:} The tech industry offers many opportunities and high demand for developers.
    \item \textbf{Impact:} Web development allows you to make an impact on businesses and individuals through innovative solutions.
  \end{itemize}
  \vspace{0.5cm}
  
\end{frame}

% Slide 4: Conclusion and Takeaways
\begin{frame}
  \frametitle{Conclusion and Takeaways}
  \begin{itemize}
    \item Web development is an exciting blend of technical and creative skills.
    \item Continuous learning and adapting to new tools and technologies is essential.
    \item Practical experience and real-world projects are crucial to becoming a successful web developer.
  \end{itemize}
  \vspace{0.5cm}
  
\end{frame}

\end{document}
